R Tools for Observations, Receptors and Footprints (rtorf)

### 2025-11-12 README.Rmd
fix obs_hysplit_control and add verbose

```{r call, include = T, message=F, warning=F}
library(rtorf)
library(data.table)
```

@@

cate = c("aircraft-pfp",
         "aircraft-insitu",
         "aircraft-flask",
         "surface-insitu",
         "surface-flask", 
         "surface-pfp",   
         "tower-insitu",  
         "aircore",       
         "shipboard-insitu",
         "shipboard-flask")

>>>>

```{r call, include = T, message=F, warning=F}
library(rtorf)
library(data.table)
utils::packageVersion("rtorf")
```

@@

cate = c(
  "aircraft-pfp",
  "aircraft-insitu",
  "aircraft-flask",
  "surface-insitu",
  "surface-flask",
  "surface-pfp",
  "tower-insitu",
  "aircore",
  "shipboard-insitu",
  "shipboard-flask"
)
